---
title: "SDS 192 2021 Fall PS07"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Section 01
## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:
```{r}
# Load all packages here
library(ggplot2)
library(dplyr)
library(babynames)
```

```{r}
# Set up the dataframe for visualization
babynames_riley_casey <- babynames %>% 
  filter((name == "Riley" | name == "Casey")) %>% 
           group_by(year)
View(babynames_riley_casey)
```

## Including Plots

You can also embed plots, for example:

```{r, echo=FALSE}
ggplot(data = babynames_riley_casey, 
       mapping = aes(x = year, y = prop, group = sex, color=sex)) +
  geom_line()+
  facet_wrap(~ name)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
